%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text - Set all text colors to black
\definecolor{darktext}{HTML}{000000}
\definecolor{text}{HTML}{000000}
\definecolor{graytext}{HTML}{000000}
\definecolor{lighttext}{HTML}{000000}

%% Hyperlink colors
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    filecolor=blue,
    citecolor=blue
}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{center}
	\headerfirstnamestyle{Maximilian} \headerlastnamestyle{Kowalski} \\
	\vspace{2mm}
	{\faEnvelope\ maxkowalski715@gmail.com} | {\faMobile\ (714)853-3574} | \href{https://www.linkedin.com/in/max-kowalski}{linkedin.com/in/max-kowalski} | \href{https://max-kowalski.com}{max-kowalski.com}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3mm}
\cvsection{Education}
\begin{cventries}
	\cventry
	{Grad Courses: Design for Manufacturability, and Mechatronics and Robotics}
	{University of Colorado, Boulder: BS in Mechanical Engineering}
	{Boulder, Colorado}
	{Aug 2019 – May 2023}
	{}
\end{cventries}

\vspace{-7mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Technical Skills}
\vspace{-3mm}
\begin{cvskills}
    \cvskill{Design/Analysis:}{SolidWorks CSWA, SolidWorks Analysis, NX, CREO, Fusion360, 6SigmaET, Mesh Editors, Various PDM Systems}
    \cvskill{Programming:}{C++, Python, Matlab, Simulink, Arduino, ROS2 Humble, MoveIt2}
    \cvskill{Engineering:}{GD\&T, DFM, DFA, Manufacturing and Assembly Instructions, Systems Engineering, Team Management}
    \cvskill{Manufacturing:}{3-axis and 5-axis CNC milling, CNC router, lathe, TIG/MIG Welding, FDM/SLS/SLA 3D printing, Bandsaw, Drill Press, Hand Tools}
\end{cvskills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Professional Experience}
\vspace{-3mm}
\begin{cventries}
    \cventry
	{Electro-Mechanical Engineer}
	{Kazvu Labs}
	{Anahiem, California}
	{May 2024 – Present}
	{\begin{cvitems}
        \item{Co-designed, built, and integrated a novel 1.8 m 7-axis collaborative robotic arm for human-centric tasks for commercial environments.}
        \item{Owned end-to-end development of three custom actuator sizes utilizing strain-wave gearboxes and 3-phase BLDC motors ($\sim$63–298 Nm), including architecture, detailed design, part selection, verification testing, manufacturing drwarings with GD\&T, and assembly instructions.}
        \item{Integrated a custom friction-pin brake, dual high-resolution absolute encoders, and precision bearing preload, and commissioned/tuned COTS motion controllers, including electrical interface design, wire harnessing, and full system-level integration.}
        \item{Analyzed joint torque data from recorded robot trajectories to ensure proper actuator sizing and reliability of brake system. Contributed to a multimodal structural optimization, analyzing robot permutations through Forward Kinematics-based workspace exploration and Jacobian analysis.}
        \item{Delivered alpha unit in 13 months at $\sim$50\% of UR10e BOM cost with +/- .5mm accuracy and 100\% workspace coverage.}
        \item{Owned setup of SolidWorks 3DEXPERIENCE PDM and a standardized, unique part numbering system and the transition to NX with an on-prem server deployment}
        \item{Architected and prototyped modular mobile robotic tooling systems to support a wide range of surface-interaction and material-handling processes.}
        \vspace{-4.5mm}
       \end{cvitems}}
    \cventry
	{Engineering Intern, Mechanical Design Engineer}
	{SV Automotive Engineering}
	{Ontario, California}
	{June 2021 - August 2021, November 2023 – May 2024}
	{\begin{cvitems}
        \item{Supported custom vehicle builds through part design, collaboration with third-party manufacturers, independent assembly projects, parts list generation, and hands-on engineering support across multiple programs.}
        \item{Designed 3D-printed electronic enclosures and engineered bespoke components for key projects, such as, a crashed Porsche 959, fully reassembling a vintage ’67 911S, and performing meticulous disassembly and diagnostics on a totaled BMW X5.}
        \item {Completed reconstruction of a scrapped car from a train crash to a SEMA design show finalist with the CSF SEMA 911 project car.}
        \item{Designed and fabricated a twin turbo, Chromoly, Pagani styled exhaust system, and installed an engine for a Martini Racing-inspired ’78 911.}
        \vspace{-2.5mm}
    \end{cvitems}}
    \cventry
	{Manufacturing Engineering Intern}
	{Eberspächer VAIREX}
	{Lafayette, Colorado}
	{June 2023 – August 2023}
	{\begin{cvitems}
        \item{Engaged in identifying and implementing process enhancements, playing a pivotal role in the reorganization and optimization of facility setups.} 
        \item{Conducted work studies to identify and address operational inefficiencies within the process.}
        \vspace{-2.5mm}
        \end{cvitems}}
    \cventry
	{Mechanical Engineering Intern}
	{Mercury Systems - Mission Systems Division}
	{Torrance, California}
	{June 2022 – August 2022}
	{\begin{cvitems}
        \item{Developed a comprehensive thermodynamic model of an avionic mission control system and a head-mounted display.}
        \item{Conducted thermal characterizations utilizing 6SigmaET, leveraging material qualities and thermodynamic equations to ensure optimal performance.}
        \item{Implemented design enhancements in Creo and SOLIDWORKS managed changes with OnePDM to optimize heat sink thermal efficiency.}
        \vspace{-1.5mm}
        \end{cvitems}}
\end{cventries}
\vspace{-5mm}
\cvsection{Engineering Projects}
\vspace{-3mm}
\begin{cventries}
	\cventry
	{CAD/Manufacturing Engineer}
	{Industry Capstone Project: Autonomous Rover for Landfill Methane Monitoring}
	{Design Center Colorado}
	{August 2022 - May 2023}
	{\begin{cvitems}
	\item {Designed and built a proof-of-concept autonomous rover for the Hannigan Air Quality Lab and Waste Management to collect SEM data in landfill environments and evaluate low-cost automation feasibility, owning all SOLIDWORKS CAD (design, revisions, drawings), FEA of critical components, fabrication/manufacturing reviews, and integration with electronics.}
 \vspace{-2.5mm}
	\end{cvitems}}
    \cventry
	{Engineering Team Leader}
	{Mobile Vision-Guided Projectile-Launching Robot Platform}
	{MCEN 5115 - Mechatronics and Robotics I}
	{August 2022 - May 2023}
	{\begin{cvitems}
	\item {Utilized a state-space model to navigate a predefined field, using sensing and OpenCV color detection to locate an opponent’s balloon, and accurately launch projectiles via a mecanum-drive platform with a high-speed flywheel launcher.}
 \vspace{-2.5mm}
	\end{cvitems}}
	\cventry
	{Engineering Team Leader}
	{Manufacturability Reports}
	{MCEN 5045 - Design for Manufacturability }
	{January 2023 - May 2023}
	{\begin{cvitems}
	\item {Led team-based manufacturability analyses on existing and new products, including reverse-engineering a Fujifilm Quicksnap Flash 400 disposable camera and designing a compact spice dispenser, using DFM/DFA, process selection, assembly and cost breakdowns, and ethical/safety considerations to improve cost and assembly efficiency.}
 \vspace{-2.5mm}
	\end{cvitems}}
\end{cventries}
\end{document}